\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=15mm, bottom=10mm, left=10mm, right=10mm]{geometry}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{titlesec}

\setlength{\parindent}{0pt}
% Define a new section format that draws a rule after the heading.
\titleformat{\section}
  {\normalfont\large\bfseries}   % format for the label and title
  {\thesection}{1em}{}
  [\vspace{0.5ex}\hrule\vspace{1ex}]  % code after the section title

\newcommand{\name}[1]{{\huge\textbf{#1}}}

\pagestyle{empty}

\begin{document}

\begin{center}
\name{Brooke E. Nazar} \\
\large{434-981-2820 \textbar{} nazarbrooke42@gmail.com} \textbar{} https://globalenvironmentalhealth.org/projects/ \\
\end{center}

\vspace{6pt}

% % Uncomment the summary if you decide to include it:
% \section*{PROFESSIONAL SUMMARY}
% I am a current student in the accelerated Master of Public Health program at Virginia Tech with a concentration in Infectious Diseases. With a strong academic background and hands-on research experience in water quality and environmental health, I am eager to apply my skills in data analysis, fieldwork, and project management to contribute to impactful public health initiatives.

\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
\section*{EDUCATION}

\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Virginia Tech} \\
\textbf{Bachelor of Science in Public Health} & \textbf{Fall 2020 -- May 2024} \\
Minor: Medicine and Society & \textit{Cum Laude} \textbar{}  GPA: 3.5 \\

\end{tabularx}


\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Accelerated Master of Public Health} & \textbf{Expected May 2025} \\
Concentration: Infectious Diseases & GPA: 3.8
\end{tabularx}

\section*{RELEVANT EXPERIENCE}

\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Cohen Research Group at Virginia Tech} & \textbf{Jan 2024 - Present}\\
\textit{Virginia Tech} & \textit{Blacksburg, VA} \\
\end{tabularx}
\begin{itemize}[leftmargin=0.75cm, noitemsep, topsep=0pt]
    \item Collected water and biospecimen samples at 30+ rural households under IRB-approved protocols to examine potential links between drinking water contaminants and health outcomes.
    \item Performed on-site water testing and subsequent lab analyses for quality assessment; acidified samples for heavy-metal testing in collaboration with external facilities.
    \item Trained 2 new field staff in household visit procedures and 4 lab assistants in water-testing protocols, streamlining the project’s workflow and enhancing data consistency.
    \item Maintained QA/QC processes by integrating survey data and lab results into Excel, identifying early trends in regional contaminant levels and health disparities relating to SES.
    \item Developed video tutorials covering field sampling and lab protocols to standardize methods for future research cohorts.
    \item Contributed to a forthcoming manuscript by performing literature reviews, interpreting preliminary findings, and drafting key sections for publication in 2025.
\end{itemize}

\section*{WORK EXPERIENCE}

\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Food Service} & \textbf{Feb 2024 - Present}\\
\textit{Virginia Tech Dining Hall} & \textit{Blacksburg, VA}
\end{tabularx}
\begin{itemize}[leftmargin=0.75cm, noitemsep, topsep=0pt]
    \item Managed daily dining hall operations and ensured strict compliance with food safety and HACCP protocols.
    \item Trained new employees in food handling procedures, enhancing operational efficiency and consistency.
    \item Coordinated inventory checks and supply ordering, reducing waste and maintaining sufficient stock during peak meal periods.
\end{itemize}

\vspace{5pt}

\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Sales Associate} & \textbf{Nov 2022 - Jan 2023}\\
\textit{TJ Maxx} & \textit{Christiansburg, VA}
\end{tabularx}
\begin{itemize}[leftmargin=0.75cm, noitemsep, topsep=0pt]
    \item Processed transactions and provided personalized customer service to enhance shopper satisfaction.
    \item Assisted with visual merchandising and maintained store organization to support brand standards and sales goals.
\end{itemize}

\vspace{5pt}


\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Baking Assistant} & \textbf{Jan 2021 - Jan 2023}\\
\textit{Henry Hudson Granola Company} & \textit{Palmyra, VA}
\end{tabularx}
\begin{itemize}[leftmargin=0.75cm, noitemsep, topsep=0pt]
    \item Baked, processed, packaged, and shipped granola products in strict adherence to food safety and sanitation standards.
    \item Maintained rigorous cleanliness throughout production and storage areas, performing routine cleaning and closing duties.
    \item Assisted in quality control checks to ensure consistent product quality and compliance with HACCP protocols.
\end{itemize}

\vspace{5pt}

\noindent
\begin{tabularx}{\textwidth}{X r}
\textbf{Customer Service Associate} & \textbf{Apr 2020 - Sep 2020}\\
\textit{CVS Pharmacy} & \textit{Palmyra, VA}
\end{tabularx}
\begin{itemize}[leftmargin=0.75cm, noitemsep, topsep=0pt]
    \item Assisted customers with inquiries and transactions to ensure an efficient and positive shopping experience.
    \item Maintained a clean, organized store environment, contributing to overall store performance.
\end{itemize}

\vspace{5pt}

\section*{SKILLS \& AWARDS}
\begin{itemize}[leftmargin=0.75cm, noitemsep, topsep=0pt]
    \item Excellent communication skills for effective interaction with colleagues and diverse stakeholders.
    \item Strong attention to detail and commitment to maintaining food safety and sanitation standards.
    \item Consistent academic excellence, evidenced by placement on the Dean's List for the Fall and Spring semesters of 2021, 2022, and 2023.
    \item Active member of the Virginia Public Health Association and the American Public Health Association.
    \item Attended the 2023 Virginia Public Health Association conference (Richmond, VA) and the 2023 American Public Health Association conference (Atlanta, GA).
\end{itemize}

\end{document}